PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-06-12 paper_review/response_20200605.txt

Dear Dr. Shafter,

We thank you for organizing the review of our paper, and also
thank the referee for their helpful comments.  We have
considered the referee's remarks carefully and revised our
manuscript accordingly.

Below, we have reproduced the relevant portions of the
referee's report, alongside our responses. A list of changes is
appended to the manuscript using the trackchanges AASTeX
macros.

Sincerely,

Luke Bouma

******************************************
REFEREE COMMENT
----------
Overall: It would help if the authors used hours or days throughout the paper
in a consistent manner. The period is referred to as 0.5d and 11.98h just a
couple paragraphs apart (e.g. in Section 5.1). The abstract uses hours, most
plots use days.

RESPONSE
----------
> Throughout the manuscript, we have shifted the units wherever possible to
> hours.
>
> Exceptions include the ephemeris (which is quoted in days), and the periods
> listed in Figures 3 and 6, which are quoted in days. The former is standard
> convention. The latter was because we felt it important to list the periods
> used to generate the figures at a higher precision, and quoting higher
> precision in units of hours seems atypical in a field in which days are more
> typically seen.

******************************************
REFEREE COMMENT
----------

Introduction: The introduction takes a light/jovial tone, e.g., did they
actually wish it were a planet, or is it more that they aimed to confirm it and
found the opposite? I would normally suggest making more formal. However, I
enjoyed reading it. I'm sorry the authors ruined their own favorite planet.

RESPONSE
----------
> So are we!  Our aim was to clarify what could be happening in the system, and
> hopefully this contribution is valuable for that.  When a planetary door
> closes, a window on young star variability opens...

******************************************
REFEREE COMMENT
----------

Introduction: I do not think this is youngest hot Jupiter. That should be true
just for transiting systems, and it was the youngest at discovery, but the two
RV planets from ESPaDOnS are younger (Donati et al. 2016 and Yu et al. 2017).
Both are hot Jupiters and in Taurus. I believe the age of Tap 26 is more
ambiguous due to age spreads (multiple groups?) in Taurus, but the age of V830
Tau is certainly <3 Myr.

RESPONSE
----------

> Thank you for this correction. We have qualified the relevant sentence as the
> youngest known *transiting* hot Jupiter. We have opted to not cite the V830
> Tau or TAP 26 results, which we hope to see confirmed by independent groups.

******************************************
REFEREE COMMENT
----------

Introduction: I also think it wasn't the first H-alpha detection. That belongs
to LkCa15, which was imaged in H-alpha in 2015 (Sallum et al. 2015). Although
that planet might not exist, so this comment is probably OK. It would still be
the first close-in planet either way. I'd suggest weakening the statement
slightly to err on the side of caution.

RESPONSE
----------
> We have changed the wording to err on the side of caution, and qualify it as
> the first direct detection of Hα emission from a close-in planet.

******************************************
REFEREE COMMENT
----------

Introduction: Barnes et al. (2013) claimed that the planet and star precessed
on a period of 300-600 days, and that this could somewhat fit variable depths
and missing transits. The Ciardi et al. 2015 paper uses this as their model, in
addition to gravity darkening as mentioned in the current introduction. I
suggest mentioning the precession of the planet in the introduction, as many
papers used the precession model or at least discussed it. The line "...the
gravity-darkened star precessed..." seems to allude to this, but it's unclear
from the rest of the text.

RESPONSE
----------
> We have changed the wording of the last sentence of the first paragraph in
> the introduction to explicitly use the word "precess", rather than "torque".

******************************************
REFEREE COMMENT
----------

Section 2: The first paragraph discusses the full frame images, while the next
section discusses the 2m data. Why did the authors use the FFIs when they have
the (higher quality) 2m data?

RESPONSE
----------
> For the essential analysis of the study (i.e., extracting and fitting the
> long and short signals), we used the 2m SPOC lightcurve.
>
> We primarily mention our use of the FFI lightcurves in Section 2 because of
> the systematic jump mentioned at BJD 2458488.3, which was eventually excluded
> from further analysis. We wanted to be sure though that this jump was truly
> an instrumental systematic, and not a software systematic. Checking
> lightcurves from independent pipelines meets this goal.
>
> A secondary reason to introduce the concept of FFIs in Section 2 is that they
> are used to measure the variability amplitudes of the other members of 25
> Ori-1 in Section 4.3.

******************************************
REFEREE COMMENT
----------

Section 2.2.2: "These details concerning the group membership for one object
may seem excessive to those accustomed to the simple distinction between "young
cluster members" and "old field stars"." I suggest removing this. It's not
adding anything and sounds like the authors are making assumptions about the
reader. The membership of this object is essential for an age assessment, and
can/should be updated given the new Gaia data. Since most of the object class
in question are at similar ages, this directly relates to the study. If it had
turned out to be ~100 Myr, we would all be more skeptical (although ~100 Myr
stars like this are known, they are more rare).

RESPONSE
----------
> We've removed it -- thank you for the suggestion.

******************************************
REFEREE COMMENT
----------

Section 3/4: This deals mostly with identification of the second star. However,
the second star appears to be an assumption of section 3.2. If the periods come
from two stars that could be separated (e.g., wide binaries), it would have
been best to do so rather than try to model both by including fs and fl terms.
So it is odd that the binary search is after the light curve model in the
paper. It might make more narrative sense to move the light curve model to
after section 4, since 4 motivates 3.2.

RESPONSE
----------
> While we see the referee's point, we prefer the narrative structure of
> presenting the TESS data first, and getting into considerations of stellar
> binarity, both resolved and unresolved, afterwards.
>
> The reasons are that i) we wrote the paper primarily because of the TESS
> data; ii) the multiple signals come from TESS data. From a story-telling
> perspective, why would we worry about binarity if we didn't already know
> there were multiple signals?

******************************************
REFEREE COMMENT
----------

Section 4.3: My biggest concern with this analysis is reliance on the chi^2
from Gaia to assess binarity. This is not the suggested path from Gaia, as it
is subject to a noise model Gaia now knows has issues. For example, nearly 100%
of mid/late M dwarfs have a high chi^2 (and a large excess astrometric noise),
but clearly they are not all binaries. This is (partially) because of a
color-term in the PSF model that was not initially understood. Similarly,
almost all bright stars have a large RUWE, as do the bluest stars. The authors
correctly use RUWE, the suggested method, but the RUWE analysis is less
convincing and clearly the authors are leaning on the chi^2.

A good reference on this would be Belokurov et al. 2020, which shows what kinds
of binaries RUWE can and cannot detect. This binary might simply be too tight
to create an astrometric signal (in which case the RUWE makes sense). The
typical cutoff for binarity is a RUWE of ~1.4, see Rizzuto et al. 2018, Ziegler
et al. 2019, Pearce et al. 2020, among many others.  I suggest removing the
chi^2 analysis. If the authors want to keep it, they need to argue why it is a
more meaningful metric than RUWE, and attempt to account for color and other
parameters that impact chi^2.

RESPONSE
----------
> We've done as suggested, and replaced this sub-plot with RUWE instead of
> reduced chi^2. The text in Section 4.3 and captions have been updated
> accordingly, and chi^2 is now mostly ignored.

******************************************
REFEREE COMMENT
----------

Section 4.4:
Need a period between velocities and Further.

RESPONSE
----------
> Corrected, thank you.

******************************************
REFEREE COMMENT
----------

Section 5.2: That clear offset at (Pl-Ps)/Ps doesn't seem like a coincidence,
and the paper reads like the authors agree, but couldn't explain it. I'm not
sure I can help much here, although it is interesting. Could this be that both
stars are dippers and one turns off while the other turns on by coincidence?
Spots and hot-spot clusters can shift in phase as the magnetic fields realign,
which creates a new spot cluster at the same period but a different phase. If
it is circumstellar material, a tight binary could be shepherding the material,
but I think the systems would have to be very tight for that, and it could not
last for such a long time.

I think this can be assessed statistically; given the scatter in those points,
the odds of lining up to any given line is small. But without a physical
explanation this is hard to test. Probably this requires looking at many
dippers as an ensemble. It is not required for the primary analysis of this
paper, so I will defer to the authors if they want to dig deeper on this.

RESPONSE
----------
> We're not sure whether or not it is a coincidence, but it seemed interesting
> enough to mention.
>
> ..

******************************************
REFEREE COMMENT
----------

Section 5.3.2: The difference between the fraction of transient flux dip stars
and the binary fraction is more significant than it appears to the authors.
High mass ratio binaries would not be included, as they are too faint to detect
the second period. Further, at the distance of Upper Sco (~150pc) and assuming
Stauffer et al. 2017 would notice/separate two stars wider than a K2 pixel
(4"), the presence of two periods would not include binaries wider than 600pc.
Eyeballing the Winters et al. 2019 distribution suggests ~20% of binaries are
beyond this. Stauffer et al. 2017 also probably checked against existing
imaging data for obvious binaries down to 1-2", so likely even more are getting
cut.

RESPONSE
----------
>

******************************************
REFEREE COMMENT
----------

Section 5.4: The authors conclude this subsection with a reasonable argument
that this isn't a protoplanet. Does this same argument not rule out gas/debris
at the Keplerian coronation radius? What could maintain such clouds for
years/decades and then have them jump phase but at the same period? It's hard
to do this if it is not somehow physically attached to the star in some what
(e.g., spots can do this).

RESPONSE
----------
>

******************************************
ADDITIONAL CHANGES

A few additional changes are noted in the "List of Changes" appended at the end
of the manuscript.

We modified the text throughout to clarify that Stauffer+ 2017 favored the
explanation of a clumpy torus of gas and dust at the Keplerian co-rotation
radius, rather than our initial (incomplete) description of "clouds of gas" at
the same location.

We also modified the labels of the axes in Figure 5a for clarity.

### 2020-06-12 paper/ms.tex
WIP for the referee report
added some nice details to flesh out the torus of gas+dust in favor of
the starspot occultations

\documentclass[12pt,twocolumn,tighten]{aastex62}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

We wish \ptfob\ were a planet. It would be quite exceptional. It would
be the youngest known hot Jupiter \citep{van_eyken_ptf_2012}, orbiting
a T Tauri star in the Orion-OB1a cluster.  It would have the shortest
orbital period of any hot Jupiter.  With such a short period, it would
probably be filling its Roche lobe, and actively losing mass to its
host star.  Not only that, but the rapidly-rotating host star is
probably oblate enough to torque the planet's orbit into and out of
the transiting configuration on a timescale of years
\citep{barnes_measurement_2013,ciardi_followup_2015,kamiaka_revisiting_2015}.

Another first would be the direct detection of H$\alpha$ emission from
the planet itself \citep{johnskrull_h_2016}.  In addition to the
chromospheric H$\alpha$ emisson, it seems that there is an additional
H$\alpha$ emission with radial velocity variations in phase with the
planetary orbit.  The average velocity width of the excess H$\alpha$
emission is 87$\,$km$\,$s$^{-1}$, and its equivalent width is 70-80\%
that of the stellar chromosphere \citep{johnskrull_h_2016}.  The
proposed explanation is that the emission is from hot material flowing
away from the planet \citep{johnskrull_h_2016}.

@@

While the planetary interpretation clearly faces challenges, there is
no completely satisfactory alternate explanation.  Low-latitude
starspots, hot or cold, would struggle to produce photometric features
as short as some of the observed dips.  High-latitude accretion
hotspots might produce the observed H$\alpha$ variability, but require
fine-tuning to produce dips of the appropriate duration.  Transits by
dust clumps or other dusty features are questionable because \ptfo\
does not have a detectable infrared (IR) excess associated with the
presence of warm dust \citep[{\it e.g.},][Figure~18]{yu_tests_2015}.
In addition, the sublimation times for dust grains of plausible
composition are quite short \citep{zhan_complex_2019}.

A relevant fact is that between 0.1\% and 1\% of rapidly rotating
low-mass stars in $\mathcal{O}$(10)$\,$Myr old associations show
short-duration dips as part of their overall periodic variability
\citep{rebull_usco_2018}.  The dips can persist over months, but their
depths often vary, and sometimes change immediately after stellar
flares.  The explanation proposed by \citet{stauffer_orbiting_2017}
and \citet{david_transient_2017} to explain this novel class of
variable stars is that a circumstellar cloud of gas is orbiting near
the co-rotation radius.  To this point, though, it has not been clear
if this explanation applies to \ptfo, because the determination of the
stellar rotation period has been somewhat ambiguous
\citep{van_eyken_ptf_2012,koen_multicolour_2015,raetz_yeti_2016}.

@@

These details concerning the group membership for one object may seem
excessive to those accustomed to the simple distinction between
``young cluster members'' and ``old field stars''.  Although all
members of the Orion complex are indeed young relative to the field,
these details are essential for assessing the photometric evidence for
the binarity of \ptfo, because of the degeneracy between stellar
luminosity and age for pre-main-sequence stars.  Having a clean sample
of reference stars that are tightly associated with \ptfo\ --- both
spatially and kinematically --- minimizes contamination not only from
field stars, but also from older and younger members of the Orion
complex.

@@

Our initial inspection of the TESS light curve, in both its 2-minute
PDCSAP and 30-minute FFI forms, showed a strong sinusoidal beat signal
(Figures~\ref{fig:splitsignal} and~\ref{fig:splitsignalii}, top
panel). As a precursor to more detailed analysis, we calculated
generalized Lomb-Scargle periodograms using \texttt{astrobase}
\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015,bhatti_astrobase_2018}.
The tallest peak occurs at 0.499\,d (11.98$\,$hr) and a second strong
peak occurs at 0.448\,d (10.76$\,$hr). We will refer to these two
periods as the ``longer period'' $P_{\rm \ell}$ and the ``shorter
period'' $P_{\rm s}$.  Lower-power harmonics of both signals are also
present.

@@

		\vspace{-0.7cm}
		\subfloat{
			\includegraphics[width=0.7\textwidth]{f5b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Evidence for binarity in \ptfo}.
    {\it Top:} Hertzsprung-Russell diagram of \ptfo\ and late-type
    members of 25$\,$Ori-1. Black circles are members of the
    25$\,$Ori-1 group identified by \citet{kounkel_apogee2_2018}.
    Gray circles are stars in the ``neighborhood'', i.e., non-member
    stars for which the right ascension, declination, and parallax are
    within 5 standard deviations of the mean values for 25$\,$Ori-1.
    The neighborhood contains members of the Orion complex with its
    full spread of ages, in addition to field interlopers.  $G$
    denotes the Gaia broadband magnitude, $Bp$ Gaia blue, $Rp$ Gaia
    red, and $\omega_{\rm as}$ the parallax in arcseconds.  The
    $x$-axis limits are chosen to display only the K and M dwarfs,
    accentuating \ptfo's separation from the single-star sequence.
    {\it Bottom:} Astrometric goodness-of-fit versus $Rp$ magnitude
    for 25$\,$Ori-1 members.  The single-source astrometric model for
    \ptfo\ provides a poor fit to the data, which could be due to
    either stellar variability or binarity.  But since cluster members
    that are at least as variable as \ptfo\ show lower astrometric
    excesses (black squares), binarity is the likely reason.
		\label{fig:gaia}
	}
\end{figure*}

@@

A separate line of evidence for binarity is the Gaia DR2 astrometry.
As noted in Section~\ref{sec:observations}, the Gaia DR2 astrometric
solution for \ptfo\ shows a 10.3$\sigma$ ``astrometric excess'', a
parameter that quantifies the degree to which a single-star model
fails to fit the astrometric measurements.  Specifically, the
single-source astrometric model yielded $\chi^2=325.2$.  There are 121
astrometric measurements, and 5 free parameters, and therefore 116
degrees of freedom. The reduced $\chi^2$ is 2.80.  The majority of
stars with comparable brightness in Gaia do not show such poor
goodness-of-fit \citep[see][Appendix A]{lindegren_gaiasoln_2018}.

Potential explanations for the poor astrometric fit include
photometric variability and unresolved stellar binarity \citep[{\it
e.g.},][]{rizzuto_ZEIT8_2018,belokurov_unresolved_2020}.  If
photometric variability were the cause, we would expect stars of
similar brightness in the same kinematic group of Orion to show
similar astrometric excesses, because the majority of young stars are
highly variable.

Using the same 149 members in the 25$\,$Ori-1 subgroup, we calculated
the astrometric reduced $\chi^2$ for each member.  We then queried the
CDIPS light curve database at MAST \citep{bouma_cluster_2019} to find
the subset of members that were at least as variable as \ptfo.  We
measured the variability amplitude by taking the difference between
the $95^{\rm th}$ and $5^{\rm th}$ percentiles of the flux
measurements.  This yielded 30 stars of equal or greater variability.
The lower panel of Figure~\ref{fig:gaia} shows the reduced $\chi^2$ as
a function of stellar brightness.  \ptfo\ is in the upper 90$^{\rm
th}$ percentile of stars showing astrometric excesses within the
25$\,$Ori-1 group.  Relative to other M-dwarf group members with
comparable brightnesses and variability characteristics, \ptfo\ still
stands out by virtue of its failure to conform to a single-star
astrometric model. This supports the interpretation that \ptfo\ is a
binary star.

Performing the same analysis using the renormalized unit weight error
(RUWE\footnote{ See the Gaia DPAC technical note
GAIA-C3-TN-LU-LL-124-01,
\url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}, accessed
2020-04-27. }) rather than the reduced $\chi^2$ yielded similar
results.  \ptfo\ has a RUWE of 1{.}22, which corresponds to the
93$^{\rm rd}$ percentile of 25$\,$Ori-1 members.  Two of thirty stars
with variability amplitudes greater than 9.7\% showed higher RUWE.
One was CVSO~35, which has a TESS light curve that varies by 2
magnitudes.  CVSO~35 also shows a strong Wide-field Infrared Survey
Exoplorer (WISE, \citealt{wright_WISE_2010}) IR excess as well as a
10$\mu$m silicate emission feature \citep{mauco_herschel_2018}.  The
other is GAIA DR2 3222210363837122048.

@@

Radial velocity (RV) measurements over sufficiently long timescales
could also reveal the presence of multiple stars in this system.
Unfortunately, the available RV data for \ptfo\ is sparse, presumably
due to the difficulties of performing RV observations of such a faint
and rapidly rotating star.  The RV datasets with the longest time
baselines we could find in the literature were those reported by
\citet{van_eyken_ptf_2012}.  These included 5 Keck/HIRES measurements
acquired over 10 days in April 2011, and 4 HET/HRS measurements
acquired over 10 days in February 2011.  The root-mean-squared RV over
each 10-day span was $\approx$$2\,{\rm km}\,{\rm s}^{-1}$, consistent
with the measurement precision.  Although \citet{van_eyken_ptf_2012}
tried a CCF-based RV reduction technique, they eventually found that
manually selecting absorption lines and measuring line centroids was
more effective.  While \citet{yu_tests_2015} acquired 22 further
Keck/HIRES spectra over one night in December 2013, those points were
not reduced to velocities. Further radial-velocity observations could
potentially confirm or refute the presence of binary companions.

@@

In their report on the discovery of the unusual photometric
variability, \citet{van_eyken_ptf_2012} saw an alias of the
longer-period signal ({\it e.g.}, their Figure~7), in the form of a
peak in the periodogram at $0.9985 \pm 0.0061\,$days. They ascribed it
to their observing cadence, because of its close correspondence to the
sidereal day.  Our pixel-level analysis showed that the signal is
specific to only pixels near \ptfo, and no other pixels.  We therefore
conclude that the signal is not an artifact of systematic errors.

We are not the first to reach the conclusion that the long period
sinusoidal modulation is astrophysical.  \citet{koen_multicolour_2015}
identified the same modes and aliases as \citet{van_eyken_ptf_2012},
and argued that the signal was astrophysical, even if the exact period
was still unclear.  Using photometry from the YETI global telescope
network, \citet{raetz_yeti_2016} came to the conclusion that the
$0.50\,{\rm d}$ signal was indeed from stellar rotation.  The TESS
data strongly support this conclusion.

@@

When physical explanations are not forthcoming, we often resort to
taxonomy.  By searching the literature, we have found about a dozen
light curves with similar morphologies to \ptfo, drawn from surveys of
low-mass weak-lined T Tauri stars in regions including $\rho$ Oph,
Upper~Sco, Taurus, and perhaps the Pleiades
\citep{rebull_rotation_2016,david_transient_2017,stauffer_orbiting_2017,stauffer_rotevol_2018,rebull_usco_2018,rebull_rotation_2020}.
These surveys were performed using K2 \citep{howell_k2_2014}.  We
downloaded some of these light curves from MAST, opting for the
EVEREST reductions \citep{luger_everest_2016,luger_update_2018}.  They
are plotted in Figure~\ref{fig:brethren}.

>>>>

%\documentclass[12pt,twocolumn,tighten]{aastex62}
\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

We wish \ptfob\ were a planet. It would be quite exceptional. It would
be the youngest known \added{transiting} hot Jupiter \citep{van_eyken_ptf_2012}, orbiting
a T Tauri star in the Orion-OB1a cluster.  It would have the shortest
orbital period of any hot Jupiter.  With such a short period, it would
probably be filling its Roche lobe, and actively losing mass to its
host star.  Not only that, but the rapidly-rotating host star is
probably oblate enough to \replaced{torque the planet's orbit into and out of
the transiting configuration}{cause the planet's orbit to precess into and out of the 
transiting configuration} on a timescale of years
\citep{barnes_measurement_2013,ciardi_followup_2015,kamiaka_revisiting_2015}.

Another first would be the direct detection of H$\alpha$ emission from
\replaced{the planet itself}{a close-in planet} \citep{johnskrull_h_2016}.  In addition to the
chromospheric H$\alpha$ emisson, it seems that there is an additional
H$\alpha$ emission with radial velocity variations in phase with the
planetary orbit.  The average velocity width of the excess H$\alpha$
emission is 87$\,$km$\,$s$^{-1}$, and its equivalent width is 70-80\%
that of the stellar chromosphere \citep{johnskrull_h_2016}.  The
proposed explanation is that the emission is from hot material flowing
away from the planet \citep{johnskrull_h_2016}.

@@

While the planetary interpretation clearly faces challenges, there is
no completely satisfactory alternate explanation.  Low-latitude
starspots, hot or cold, would struggle to produce photometric features
as short as some of the observed dips.  High-latitude accretion
hotspots might produce the observed H$\alpha$ variability, but require
fine-tuning to produce dips of the appropriate duration.  Transits by
dust clumps or other dusty features are questionable because \ptfo\
does not have a detectable infrared (IR) excess associated with the
presence of warm dust \citep[{\it e.g.},][Figure~18]{yu_tests_2015}.
In addition, the sublimation times for dust grains of plausible
composition \replaced{are}{could be} quite short \citep{zhan_complex_2019}.

A relevant fact is that between 0.1\% and 1\% of rapidly rotating
low-mass stars in $\mathcal{O}$(10)$\,$Myr old associations show
short-duration dips as part of their overall periodic variability
\citep{rebull_usco_2018}.  The dips can persist over months, but their
depths often vary, and sometimes change immediately after stellar
flares.  The explanation proposed by \citet{stauffer_orbiting_2017}
and \citet{david_transient_2017} to explain this novel class of
variable stars is that a \replaced{circumstellar cloud of gas is orbiting near
the co-rotation radius}{clumpy torus of dust and gas orbits near the
Keplerian co-rotation radius}.  To this point, though, it has not been clear
if this explanation applies to \ptfo, because the determination of the
stellar rotation period has been somewhat ambiguous
\citep{van_eyken_ptf_2012,koen_multicolour_2015,raetz_yeti_2016}.

@@

\replaced{These details concerning the group membership for one object may seem
excessive to those accustomed to the simple distinction between
``young cluster members'' and ``old field stars''.  Although all
members of the Orion complex are indeed young relative to the field,}
{While all members of the Orion complex are young relative to the field,}
these \replaced{details}{considerations} are essential for assessing \deleted{the} photometric evidence for
the binarity of \ptfo, because of the degeneracy between stellar
luminosity and age for pre-main-sequence stars.  Having a clean sample
of reference stars that are tightly associated with \ptfo\ --- both
spatially and kinematically --- minimizes contamination not only from
field stars, but also from older and younger members of the Orion
complex.

@@

Our initial inspection of the TESS light curve, in both its 2-minute
PDCSAP and 30-minute FFI forms, showed a strong sinusoidal beat signal
(Figures~\ref{fig:splitsignal} and~\ref{fig:splitsignalii}, top
panel). As a precursor to more detailed analysis, we calculated
generalized Lomb-Scargle periodograms using \texttt{astrobase}
\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015,bhatti_astrobase_2018}.
The tallest peak occurs at \replaced{0.499\,d (11.98$\,$hr)}{11.98$\,$hr} and a second strong
peak occurs at \replaced{0.448\,d (10.76$\,$hr)}{10.76$\,$hr}. We will refer to these two
periods as the ``longer period'' $P_{\rm \ell}$ and the ``shorter
period'' $P_{\rm s}$.  Lower-power harmonics of both signals are also
present.

@@

		\vspace{-0.7cm}
		\subfloat{
			\includegraphics[width=0.7\textwidth]{f5b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Evidence for binarity in \ptfo}.
    {\it Top:} Hertzsprung-Russell diagram of \ptfo\ and late-type
    members of 25$\,$Ori-1. Black circles are members of the
    25$\,$Ori-1 group identified by \citet{kounkel_apogee2_2018}.
    Gray circles are stars in the ``neighborhood'', i.e., non-member
    stars for which the right ascension, declination, and parallax are
    within 5 standard deviations of the mean values for 25$\,$Ori-1.
    The neighborhood contains members of the Orion complex with its
    full spread of ages, in addition to field interlopers.  $G$
    denotes the Gaia broadband magnitude, $Bp$ Gaia blue, $Rp$ Gaia
    red, and $\omega_{\rm as}$ the parallax in arcseconds.  The
    $x$-axis limits are chosen to display only the K and M dwarfs,
    accentuating \ptfo's separation from the single-star sequence.
    {\it Bottom:} Renormalized astrometric
    unit weight error (RUWE) versus $Rp$ magnitude
    for 25$\,$Ori-1 members.  The single-source astrometric model for
    \ptfo\ provides a poor fit to the data, which could be due to
    either stellar variability or binarity.  But since cluster members
    that are at least as variable as \ptfo\ show lower astrometric
    excesses (black squares), binarity is the likely reason.
		\label{fig:gaia}
	}
\end{figure*}

@@

\explain{All paragraphs in this section have been heavily
	reworded to emphasize RUWE over $\chi_{\rm red}^2$, as requested by the
	referee.}
A separate line of evidence for binarity is the Gaia DR2 astrometry.
As noted in Section~\ref{sec:observations}, the Gaia DR2 astrometric
solution for \ptfo\ shows a 10.3$\sigma$ ``astrometric excess'', a
parameter that quantifies the degree to which a single-star model
fails to fit the astrometric measurements.  Specifically, the
single-source astrometric model yielded $\chi^2=325.2$.  There are 121
astrometric measurements, and 5 free parameters, and therefore 116
degrees of freedom. The reduced $\chi^2$ is 2.80.  While the majority of
stars with comparable brightness in Gaia do not show such poor
goodness-of-fit\added{, many M dwarfs do, because of a color-dependent
term in the mission's PSF model} \citep[see][Appendix A]{lindegren_gaiasoln_2018}.
The reduced $\chi^2$ has been
``renormalized'' to account for this, yielding a modified
statistic called the renormalized unit weight error
(RUWE\footnote{ See the Gaia DPAC technical note
	GAIA-C3-TN-LU-LL-124-01,
	\url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}, accessed
	2020-04-27. }).

We acquired the RUWE for each of the
149 members in 25$\,$Ori-1 identified by
identified by \citet{kounkel_apogee2_2018}.
We then queried the
CDIPS light curve database at MAST \citep{bouma_cluster_2019} to find
the subset of members that were at least as variable as \ptfo.  We
measured the variability amplitude by taking the difference between
the $95^{\rm th}$ and $5^{\rm th}$ percentiles of the flux
measurements.  This yielded 30 stars of equal or greater variability.
The lower panel of Figure~\ref{fig:gaia} shows the RUWE of
these stars as
a function of stellar brightness.  \ptfo\ is at the 93$^{\rm
	rd}$ percentile of equally-variable stars within the
25$\,$Ori-1 group.  
Two of the thirty stars
with variability amplitudes greater than 9.7\% showed higher RUWE.
One was CVSO~35, which has a TESS light curve that varies by 2
magnitudes.  CVSO~35 also shows a strong Wide-field Infrared Survey
Exoplorer (WISE, \citealt{wright_WISE_2010}) IR excess as well as a
10$\mu$m silicate emission feature \citep{mauco_herschel_2018}.  The
other star was GAIA DR2 3222210363837122048.

Potential explanations for an elevated RUWE include
photometric variability and unresolved stellar binarity \citep[{\it
e.g.},][]{rizzuto_ZEIT8_2018,belokurov_unresolved_2020}.  
If photometric variability were the root cause, we would expect stars with
similar brightness and color in the same kinematic group of Orion to show
similar astrometric excesses, because the majority of young stars are
highly variable.
However
relative to other M-dwarf group members with
comparable brightnesses and variability characteristics, \ptfo\ still
stands out by virtue of its failure to conform to a single-star
astrometric model. This supports the interpretation that \ptfo\ is a
binary star.

@@

Radial velocity (RV) measurements over sufficiently long timescales
could also reveal the presence of multiple stars in this system.
Unfortunately, the available RV data for \ptfo\ is sparse, presumably
due to the difficulties of performing RV observations of such a faint
and rapidly rotating star.  The RV datasets with the longest time
baselines we could find in the literature were those reported by
\citet{van_eyken_ptf_2012}.  These included 5 Keck/HIRES measurements
acquired over 10 days in April 2011, and 4 HET/HRS measurements
acquired over 10 days in February 2011.  The root-mean-squared RV over
each 10-day span was $\approx$$2\,{\rm km}\,{\rm s}^{-1}$, consistent
with the measurement precision.  Although \citet{van_eyken_ptf_2012}
tried a CCF-based RV reduction technique, they eventually found that
manually selecting absorption lines and measuring line centroids was
more effective.  While \citet{yu_tests_2015} acquired 22 further
Keck/HIRES spectra over one night in December 2013, those points were
not reduced to velocities\added{.} Further radial-velocity observations could
potentially confirm or refute the presence of binary companions.

@@

In their report on the discovery of the unusual photometric
variability, \citet{van_eyken_ptf_2012} saw an alias of the
longer-period signal ({\it e.g.}, their Figure~7), in the form of a
peak in the periodogram at \replaced{$0.9985 \pm 0.0061\,$days}{$23.96\pm0.15\,$hr}. They ascribed it
to their observing cadence, because of its close correspondence to the
sidereal day.  Our pixel-level analysis showed that the signal is
specific to only pixels near \ptfo, and no other pixels.  We therefore
conclude that the signal is not an artifact of systematic errors.

We are not the first to reach the conclusion that the long period
sinusoidal modulation is astrophysical.  \citet{koen_multicolour_2015}
identified the same modes and aliases as \citet{van_eyken_ptf_2012},
and argued that the signal was astrophysical, even if the exact period
was still unclear.  Using photometry from the YETI global telescope
network, \citet{raetz_yeti_2016} came to the conclusion that the
\replaced{$0.50\,{\rm d}$}{11.98$\,$hr} signal was indeed from stellar rotation.  The TESS
data strongly support this conclusion.

@@

\explain{Note: Citations to Parks et al 2014 and Stauffer et al 2015 were
	added to the paragraph below}
When physical explanations are not forthcoming, we often resort to
taxonomy.  
By searching the literature, we found about a dozen light curves with
similar morphologies to \ptfo, drawn from surveys of low-mass
weak-lined T Tauri stars in regions including $\rho$ Oph, Upper~Sco,
Taurus, and perhaps the Pleiades
\citep{parks_periodic_2014,rebull_rotation_2016,david_transient_2017,stauffer_orbiting_2017,stauffer_rotevol_2018,rebull_usco_2018,rebull_rotation_2020}.
The clearest matches came from K2 \citep{howell_k2_2014}, but a few
analogs were potentially also found using 2MASS (YLW 1C and YLW 10C;
\citealt{parks_periodic_2014}) and CoRoT
(\citealt{stauffer_csi_2015}).  We downloaded a subset of the K2 light
curves from MAST, opting for the EVEREST reductions
\citep{luger_everest_2016,luger_update_2018}.  They are plotted in
Figure~\ref{fig:brethren}.

\explain{Note: added citation to Bodman et al 2017 in this paragraph.}
These light curves have been phenomenologically classified as
``persistent flux dips'' or ``transient flux dips'', based on whether
their depths and durations show variability over the 90-day K2
campaigns \citep{stauffer_orbiting_2017}.  In the terminology of
\citet{stauffer_orbiting_2017}, these objects are morphologically
distinct from ``scallop shell'' light curves, and are present in stars
at more advanced evolutionary disk stages than the ``dipper'' stars
\citep{ansdell_young_2016,bodman_dippers_2017,cody_manyfaceted_2018}.  The persistent and
transient flux dip stars all show angular dips that are cannot be
explained as the effects of starspots.  These stars typically have the
following things in common:
\begin{enumerate}[topsep=0.5ex,itemsep=-0.5ex,partopsep=1ex,parsep=1.5ex]
  \item They are weak-lined T Tauri stars.
  \item The spectral type is M2 to M5 ({\it e.g.},
    \citealt{rebull_usco_2018},~Figure~20).
  \item \replaced{The age is typically $\lesssim$ 100$\,$Myr.}{The
    ages typically range between 5 and 100$\,$Myr.}\footnote{ At
    present, the oldest observed ``scallops'' are in the Pleaides
    \citep{rebull_rotation_2016}. One of these, EPIC 211013604, might
    meet the ``persistent dip'' classification.  If so, it is \deleted{also} the
    oldest known. \added{The lower limit comes from the lack of detectable
   WISE infrared excesses.}} 
  \item The light curves show shallow, angular dips, \deleted{usually}
    superposed on large-amplitude smooth variability \added{at or near
    1:1 synchronicity}. The \replaced{latter}{smooth variability} is
    interpreted as stellar rotation.
  \item The rotation is rapid, with a period that is usually between
    0.5 and 2.0 days.
  \item There is rarely any infrared excess that is detectable in the
    WISE data (never any W4 detection; only a few W3 detections).
  \item They sometimes show multiple dips per cycle.
  \item The dip depths, durations, and phases can vary over just a few
    cycles ({\it e.g.}, EPIC 204143627).
  \item The dip depths can change after flares.
  \item They are rare at a population level, with an occurrence rate
  \replaced{of $\lesssim 1\%$}{between 0.1--1\%}
   of young M2-M5 stars \citep{rebull_usco_2018}.
\end{enumerate}
The 10.76$\,$hr signal in \ptfo\ meets all of these criteria.  This is
the first connection of \ptfo\ with this class of objects, likely
because the TESS data enabled us to put the dips in the context of the
asymmetric out-of-dip modulation.
